Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-27 paper/paper.qmd
Code linting and styling for the R file in the script folder and change the graph 1 code also some description

#loading packages
#install.packages("opendatatoronto")
#install.packages("tidyverse")
install.packages("here")
library(opendatatoronto)
library(tidyverse)
library(here)
```

@@

The structure of this paper is as follows: {#sec-data-overview} presents the data sources and methodology, {#sec-data-overview} presents the results of the analysis, and {#sec-discussion} discusses the policy implications of the findings, particularly with regard to how to respond to crime hotspots in Toronto.

@@

The R programming language [@citeR] and `tidyverse` [@citetidyverse] were used to simulate and test the data set. Then, use `opendatatoronto`[@citeopendatatoronto] and `tidyverse` [@citetidyverse] to download Neighbourhood Crime Rates data. Finally, `tidyverse`[@citetidyverse] is used to clean up the original data, select the required data information to clean up the data that does not meet the requirements, and test the cleaned data again.

@@

@@

# Create the plot
ggplot(filtered_data, aes(x = Year, y = TheftRate, color = AREA_NAME)) +
  geom_line() +
  labs(title = "Trends in Theft Rates (2014-2023)",
       subtitle = "Top 15 and Bottom 15 Cities by Average Theft Rate",
       x = "Year",
       y = "Theft rate per 100,000 people") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))
```
```

>>>>

#loading packages
#install.packages("opendatatoronto")
#install.packages("tidyverse")
#install.packages("knitr")
#install.packages("here")
#install.packages("kableExtra")
library(opendatatoronto)
library(tidyverse)
library(here)
library(knitr)
library(kableExtra)
```

@@

The structure of this paper is as follows: @sec-data-overview presents the data sources and methodology, @sec-data-overview presents the results of the analysis, and @sec-discussion discusses the policy implications of the findings, particularly with regard to how to respond to crime hotspots in Toronto.

@@

The R programming language [@citeR] and `tidyverse` [@citetidyverse] were used to simulate and test the data set. Then, use `opendatatoronto`[@citeopendatatoronto] and `tidyverse` [@citetidyverse] to download Neighbourhood Crime Rates data. Finally, `tidyverse`[@citetidyverse] is used to clean up the original data, select the required data information to clean up the data that does not meet the requirements, the sample of clean data can be found in @tbl-cleaned-data .Then test the cleaned data again.

@@

```{r}
#| label: tbl-cleaned-data
#| tbl-cap: Sample of cleaned lead data 
#| echo: false

# This code is based on the sample from Alexander (2023).
data1 <- crime_rates_data[,c(1, 3, 13)]

head(data1, 3) %>%
  kable(
    col.names = c("AREA_NAME", "THEFTOVER_RATE_2015", "ASSAULT_RATE_2023"),
    booktabs = TRUE
)
```

@@

# Create the plot
ggplot(filtered_data, aes(x = Year, y = TheftRate, color = AREA_NAME)) +
  geom_line() +
  labs(title = "Trends in Theft Rates (2014-2023)",
       subtitle = "Top 15 and Bottom 15 Cities by Average Theft Rate",
       x = "Year",
       y = "Theft rate per 100,000 people") +
  theme_minimal() +
  theme(legend.position = "none")
```
```
